Quality Assessment of OpenStreetMap Footpath Data

### 2020-06-24 report/report.tex
Import result table margins

\begin{table}[H]
    \begin{tabular}{lllll}
                                & Footpath      & Residential  & Secondary   & Primary     \\
        Features, total         & 26473         & 10523        & 3044        & 2756        \\
        Edges, total            & 6382579       & 6612383      & 968420      & 420810      \\
        Edge length, total      & 129984.79 km  & 186089.55 km & 29304.57 km & 16162.95 km \\
        Features, colliding     & 3189          & 1032         & 412         & 456         \\
        Edges, colliding        & 7330          & 2362         & 643         & 824         \\
        Edge length, colliding  & 110.67 km     & 66.18 km     & 9389.30 m   & 20.41 km    \\
        Features, percent       & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
        Edges, percent          & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
        Edge length, percent    & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0.13 \%

@@

% With internet
% TODO: Fix result table margins

>>>>

\begin{table}[H]
    \begin{tabular}{lllll}
                                    & Footpath      & Residential  & Secondary   & Primary     \\
        Features, total             & 26473         & 10523        & 3044        & 2756        \\
        Edges, total                & 6382579       & 6612383      & 968420      & 420810      \\
        Edge length, total (km)     & 129984.79     & 186089.55    & 29304.57    & 16162.95    \\
        Features, colliding         & 3189          & 1032         & 412         & 456         \\
        Edges, colliding            & 7330          & 2362         & 643         & 824         \\
        Edge length, colliding (km) & 110.67        & 66.18        & 0.94        & 20.41       \\
        Features, percent           & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
        Edges, percent              & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
        Edge length, percent        & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0.13 \%

@@
